IGRINS spectra of \name

### 2016-03-25 document/ms.tex
A notebook to trim the ends of IGRINS spectral orders.

A main motivating factor in designing our methodology was our wish to adress this question for a given spectrum: ``Is the spectrum consistent with the non-detection of starspots, and to what level of confidence can the detection of starspots be reported?''.  In order to answer this question, we need some way to gauge the uncertainty in the derived stellar properties, which we assumed would have some level of degeneracy.  For example, we expect the best fit effective temperature contrast will be partially degenerate with the areal coverage fraction: a slightly cooler, smaller sunspot can masquerade as a larger, warmer spot.  This degeneracy should be lessened in spectroscopic methods compared to photometric methods.  The desire to reveal these intra-parameter correlations motivated the choice of \emph{sampling} from the posterior probability density distribution function.

@@

We modified the \iancze spectral inference framework to fit $\vM$ in each spectral order \emph{independently}: $\vT \rightarrow \vT_o$, where $o$ signifies the spectral order, which could stem from multiple spectrographs, each with multiple orders.  This change does not represent reality: the star has a single set of stellar properties, which do not depend on the wavelength range at which they are measured.  The naive single-component fit to different wavelength chunks conveys information about

\begin{eqnarray} \label{eqn:scaling}
\vM(\vT_o) &=& \vM(\vt_{\ast}, \vt_{\rm ext}) \\
         &=& \vM(\vt_{\ast}, \sigma_v, v\sin{i}, v_r) \times \Omega \times 10^{-0.4\,A_{\lambda}}, \nonumber
\end{eqnarray}

star spot areal coverage fraction is very small, then the signal associated with the

>>>>

A main motivating factor in designing our methodology was our wish to adress this question for a given spectrum: ``Is the spectrum consistent with the non-detection of starspots, and to what level of confidence can the detection of starspots be reported?''.  In order to answer this question, we need some way to gauge the uncertainty in the derived stellar properties, which we assumed would have some level of degeneracy among themselves.  For example, we expect the best fit effective temperature contrast will be partially degenerate with the areal coverage fraction: a slightly cooler, smaller sunspot can masquerade as a larger, warmer spot.  This degeneracy should be lessened in spectroscopic methods compared to photometric methods.  The desire to reveal these intra-parameter degeneracies motivated the choice of \emph{sampling} from the posterior probability density distribution function.

@@

We modified the \iancze spectral inference framework to fit $\vM$ in each spectral order \emph{independently}: $\vT \rightarrow \vT_o$, where $o$ signifies the spectral order, which could stem from multiple spectrographs, each with multiple orders.  This change does not represent reality: the star has a single set of stellar properties, which do not depend on the wavelength range at which they are measured.  The na\"ive single-component fit to different wavelength could provide a plausibility argument for the presence of a second photospheric component if the derived $\vT_o$ show a spread in $\teff$.  It is conceivable that other parameters, like $\logg$ could show a dependence on wavelength if non-standard physics---\emph{i.e.}physics not included in the pre-computed model grid---mimics the effect on the spectrum.  For example, magnetic fields could cause Zeeman broadening, which could alter the derived stellar parameters $\vT_o$.  For these reasons, we intentionally allowed \emph{all} the stellar parameters $\vT_o = {T_{\mathrm{eff},o}, \logg_o, \feh_o, \sigma_{v, o}, v\sin{i}_o, v_{r,o}}$ to vary by order.  In principle, one could refine the inference in an \emph{empirical Bayes'} strategy CITE (XX, astroML book?), in which we re-evaluate $\vT_o$ by setting priors on all the stellar parameters except $T_{\mathrm{eff},o}$.  We elected not to pursue an empirical Bayes' approach.

As a side benefit, the strategy of fitting $\vT_o$ in each spectral order provides a useful check on our instrumental calibration. If the stellar parameters in one order is routinely off, we can examine and refine our instrumental calibration.  For example, the radial velocity $v_r$ could be systematically offset in one order due to instrumental calibration problems.  Or perhaps the $v\sin{i}$ could show a dependence on wavelength, since the spectral inference framework assumes the spectral resolution is a fixed across all wavelengths, but in fact there is a small dependence on wavelength.  This spectral-order granularity in fit quality is not available in a fit that includes \emph{all} $N_{order}$ spectral orders.  In fact, the benefits of spectral chunking could be made even-more-granular by chunking the spectrum into individual spectral lines or line-groups.  The fit quality could then be assessed on a line-by-line basis, even taking into account systematic effects like individual elemental abundance patterns beyond the coarse $\feh$ estimates.  Future improvements to the spectral inference framework are directed at this spectral-line chunking strategy.
